Depression and suicidality as evolved credible signals of need in social conflicts

### 2021-06-14 Paper.rmd
Added a comment in parentheses. Minor change to line 123

<!-- Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994] -->

@@

<!-- Due to the likelihood that the payoffs to deception increase with greater conflicts of interests, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly. We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners. -->

>>>>

<!-- Compared to non-depressed individuals, those with depression report about twice as many negative events [@Mazure1998] and more negative events than those with schizophrenia and bipolar depression across multiple studies [@Paykel1994] (we repeat non-depressed individuals) -->

@@

<!-- Due to the likelihood that the payoffs to deceiving one's cooperative partners increase with greater conflicts of interests, “cheap” signals of need, such as sad expressions and crying, may often not be believed when providing support is costly. We argue next that some of the most costly and mysterious symptoms of depression -- profound loss of interest in virtually all activities and suicidality -- are *credible* and adaptive signals of need when there are conflicts of interest between victims of adversity and their social partners. -->
